---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliations: 
        - id: some-tech
          name: Some Institute of Technology
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    attributes:
        corresponding: true
    notes: This is the first author footnote.
  - name: Bob Security
    email: bob@example.com
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    notes: Another author footnote
  - name: Cat Memes
    email: cat@example.com
    affiliations:
        - ref: another-u
  - name: Derek Zoolander
    email: derek@example.com
    affilations:
        - ref: some-tech
abstract: |
  This is the abstract.

  It consists of two paragraphs.
keywords: 
  - keyword1
  - keyword2
#journal: "An awesome journal"
date: last-modified
classoption: preprint, 3p, authoryear
bibliography: bibliography.bib
linenumbers: false
number-sections: true
format:
    elsevier-pdf:
        keep-tex: true
        cite-method: natbib

---

Please make sure that your manuscript follows the guidelines in the 
Guide for Authors of the relevant journal. It is not necessary to 
typeset your manuscript in exactly the same way as an article, 
unless you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>

# Bibliography styles

Here are two sample references: @Feynman1963118 [@Dirac1953888].

By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. 
You can sets extra options with `natbiboptions` variable in YAML header. Example 
```yaml
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at
<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. 
To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.

## Using CSL 

If `citation_package` is set to `default` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`. In this case, the `csl` option is used to format the references. Alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>. These can be downloaded
and stored locally, or the url can be used as in the example header.

# Equations

Here is an equation:
$$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Here is another:
\begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

Figure \ref{fig2} is generated using an R chunk.

```{r fig2, fig.width = 5, fig.height = 5, fig.align='center', out.width="50%", fig.cap = "\\label{fig2}A meaningless scatterplot.", echo = FALSE}
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in Table \ref{tab1} for example.

```{r tab1, echo = TRUE}
knitr::kable(head(mtcars)[,1:4], 
    caption = "\\label{tab1}Caption centered above table"
)
```

# References {-}
